---
title: "DEATHS BY COUNTRY"
output: 
  html_document: 
    css: style.css
lang: es-CO
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gt)
library(reactable)
library(repmis)
library(dplyr)
library(knitr)

source("code/graficos_latam.R")

Sys.setlocale(locale = "es_ES.UTF-8")
```

<h2 <span style = "color: #e61b72">
    <b>Deaths</b></span> <span style = "color: #000000">by country and per million inhabitants</span>  
</h2>

<h4>Interactive infographic: hover over the infographic and select the countries that you want to compare from the section appearing to the right.</h4>
```{r, include=T, echo = F}
millon_fallecidos
```
<small><small><small>
Our own graphic, based on data from [Johns Hopkins University](https://github.com/CSSEGISandData/COVID-19), the [World Bank](https://datos.bancomundial.org/indicador/SP.POP.TOTL), and the [CIA](https://www.cia.gov/library/publications/the-world-factbook/fields/335rank.html)
</small></small></small>
<br>
<br>

<h2 style = color: #000000;>
    New <span style = "color: #e61b72"><b>deaths</b></span> per day since Patient Zero in each country 
</h2>

<center><h4>Interactive infographic: hover over the infographic and select the countries that you want to compare from the section appearing below. The width of each color reflects that country's proportion of the total.</h4></center>

```{r, include=T, echo = F}
incidencia_fallecidos
```
<small><small><small>
<small><small><small>
Our own graphic, based on data from [Johns Hopkins University](https://github.com/CSSEGISandData/COVID-19), the [World Bank](https://datos.bancomundial.org/indicador/SP.POP.TOTL), and the [CIA](https://www.cia.gov/library/publications/the-world-factbook/fields/335rank.html)
</small></small></small>
<br>
<br>

<h2 <span style = "color: #e61b72">
    <b>Total deaths</b></span> <span style = "color: #000000">per day since Patient Zero in each country </span> 
</h2>

<center><h4>Interactive infographic: hover over the infographic and select the countries that you want to compare from the section appearing below. The width of each color reflects that country's proportion of the total.</h4></center>
```{r, include=T, echo = F}
rio_fallecidos
```
<small><small><small>
Our own graphic, based on data from [Johns Hopkins University](https://github.com/CSSEGISandData/COVID-19), the [World Bank](https://datos.bancomundial.org/indicador/SP.POP.TOTL), and the [CIA](https://www.cia.gov/library/publications/the-world-factbook/fields/335rank.html)
</small></small></small>
